---
title: "Bioshock Doc"
format: html
authors:
- J. Jedediah Smith
- Gerard Duncan
- Ian Lacy
---

## Workflow

We're a little bit uncertain about our workflow. It's terrifyingly long and we aren't quite sure where to start, but here is the link so we don't forget. <https://www.bioconductor.org/packages/release/workflows/vignettes/methylationArrayAnalysis/inst/doc/methylationArrayAnalysis.html>.

## Loading the Package

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
#| eval: false

if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("methylationArrayAnalysis")
```

## Loading the Data

This is how we loaded the example data. It is part of the package so you do not need to install anything extra. 

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).


Context & Use
Data & Structure
